---
title: "homework1_movie_scoring"
author: "jim_song 宋晉德 台北大學 碩二"
date: "2018年10月29日"
output: html_document
---

## The Library

ggplot2movies is the data of the movies scoring . ggplot2 is the graph tool. dplyr is calculation tool.

```{r lib}
  library(ggplot2movies)
  library(ggplot2)
  library(dplyr)
```

## Initialize The Class

In first , we should build the 25nd column to call "class". And there is empty string data.

```{r initialize}
m <- movies
m[,25]=""
colnames(m)[25] <- "class"
```

## Fill In The Class And Get The Head

We check the column from "Short" to "Action". If we get 1 , we will fill in the column . If we get lots of 1 , we will fill in the column that is first condition to get 1.
If we get no 1 , we won't fill anything.

```{r fill}
for(i in 1:nrow(m)){
  if(m[i,"Short"]==1){
    m[i,"class"]="Short"
  }else if(m[i,"Romance"]==1){
    m[i,"class"]="Romance"
  }else if(m[i,"Documentary"]==1){
    m[i,"class"]="Documentary"
  }else if(m[i,"Drama"]==1){
    m[i,"class"]="Drama"
  }else if(m[i,"Comedy"]==1){
    m[i,"class"]="Comedy"
  }else if(m[i,"Animation"]==1){
    m[i,"class"]="Animation"
  }else if(m[i,"Action"]==1){
    m[i,"class"]="Action"
  } 
} 
options(dplyr.width = Inf)
head(m)
```

##Graph The Class Using Bar

```{r bar}
ggplot(m,aes(class))+geom_bar()
```

##Summarise The Class Using Median

```{r summarise}
summarise(group_by(m,class),median(rating))
```
